Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-04-29 reports/manuscript/paper_changes.tex
Correct wording.

\item Diffusion MRI data from a previous study of properties of
the white matter across the lifespan \cite{yeatman2014lifespan},
containing dMRI data from 76 subjects with ages 6-50. These data were
measured in a GE Discovery 750 3T MRI scanner at the Stanford Center
for Cognitive and Neurobiological Imaging. The Stanford University
IRB approved the procedures of this study. Informed consent was
obtained from each adult participant, and assent for participation
was provided by parents/guardians for children. Voxel resolution was
\num{2x2x2}$\textrm{mm}^3$ with 96 non-colinear directions measured with a
$b=2000$ $\textrm{s} / \textrm{mm}^2$ and 30 non-colinear directions
measured with a $b=1000$ $\textrm{s} / \textrm{mm}^2$. These data
were acquired using a dual spin echo sequence, in which there is
sufficient time for eddy currents to subside between the application of
the gradients and the image acquisition, so no eddy current correction
was applied, but motion correction was applied before fitting the
diffusion tensor model \cite{basser1994mr} in every voxel using a robust
fit \cite{chang2005restore}
\added{on the \protect$b=1000$ \protect$\textrm{s} / \textrm{mm}^2$ shell only}.
We will refer to this dataset as WH.

>>>>

\item Diffusion MRI data from a previous study of properties of
the white matter across the lifespan \cite{yeatman2014lifespan},
containing dMRI data from 76 subjects with ages 6-50. These data were
measured in a GE Discovery 750 3T MRI scanner at the Stanford Center
for Cognitive and Neurobiological Imaging. The Stanford University
IRB approved the procedures of this study. Informed consent was
obtained from each adult participant, and assent for participation
was provided by parents/guardians for children. Voxel resolution was
\num{2x2x2}$\textrm{mm}^3$ with 96 non-colinear directions measured with a
$b=2000$ $\textrm{s} / \textrm{mm}^2$ and 30 non-colinear directions
measured with a $b=1000$ $\textrm{s} / \textrm{mm}^2$. These data
were acquired using a twice refocused spin echo sequence, in which there is
sufficient time for eddy currents to subside between the application of
the gradients and the image acquisition, so no eddy current correction
was applied, but motion correction was applied before fitting the
diffusion tensor model \cite{basser1994mr} in every voxel using a robust
fit \cite{chang2005restore}
\added{on the \protect$b=1000$ \protect$\textrm{s} / \textrm{mm}^2$ shell only}.
We will refer to this dataset as WH.
